---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Travis-CI Build Status](https://travis-ci.org/vadimus202/datatableEZ.svg?branch=master)](https://travis-ci.org/vadimus202/datatableEZ)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/vadimus202/datatableEZ?branch=master&svg=true)](https://ci.appveyor.com/project/vadimus202/datatableEZ)


## A Friendly Datatable

`datatable_EZ()` is a wrapper around `DT::datatable()` with more convenient defaults. Also, most common elements of the `options()` argument are moved to direct arguments list for this function. This removes to necessity to pass on long options list (which is not well documented in the `DT` package documentation). It also makes these options available for auto-complete drop-downs in RStudio.

Read the **Interactive Data Tables** vignette for some examples.

```{r, eval=FALSE}
library(datatableEZ)
```

### Original datatable

- Includes row numbers by default
- Less compact
- Options are not well documented

```{r, eval=FALSE}
datatable(iris)
```


### Easy Datatable

- By default:
    - More compact
    - No row numbers
    - Search highlights
- Direct access to options through named arguments:
    - DOM elements
    - Column definitions (width, alignment, etc.)
    - Rows sorting
    - Page length

```{r, eval=FALSE}
datatable_EZ(
    iris,
    dom="t",
    columnDefs = list(list(width = '50px', targets = c(1, 3))),
    order = list(list(0, 'desc'), list(1, 'asc'))
)
```


### Pagination

- Number of rows per page
- Page length drop-down options
```{r, eval=FALSE}
datatable_EZ(iris, pageLength = 3, lengthMenu = c(3,5,10))
```



### Static Version

Disables sorting and searching by the user.
```{r, eval=FALSE}
datatable_EZ(iris, ordering = FALSE, dom = "t")
```


### Conditional Databars

A simple way to add conditional formatting databars to one or more columns.

```{r, eval=FALSE}
iris %>% 
    datatable_EZ() %>% 
    format_databars(~Sepal.Length + Sepal.Width + Petal.Length)
```


